Airspace configuration decision based on Monte-Carlo tree search

### 2018-04-26 article/article.tex
(+) results

In this paper, each partition scheme is based upon the number of aircraft in
each
elementary module and the cost of transition from the previous partitioning. The
available partitions come from a predetermined set containing feasible
partitionings.

@@

\subsection{Theoretical performances}
In this paper, we consider a high branching factor problem.

Let \(M\) be the number of edges between the inital state and a final state and
\(K\) the branching factor.
Then, the complexity of the A\(^*\) is expected to be, in the worst case,
exponential in \(M\) (see~\cite{alliotschiex2002ia&it}).

Since the Monte carlo tree is a stochastic method, one must wait for a
satisfactorily converging solution rather than the exact solution. It has
however been proven in~\cite{kocsis2006bandit} that the bias of the expected
payoff is \(O\left(\frac{\log n}{n}\right)\). Furthermore, the failure
probability\footnote{probability of not selecting the best child} converges to
zero at a polynomial rate.

@@

>>>>

@@

@@

\section{Results}

TODO
